Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-11 robdml.tex
tex

\noindent\textbf{III. Intra-Class Structure.}
%
$L_\text{ICS}$ is independent to HM, but is incompatible with ACT as it
does not create adversarial anchor.
%
Thus, we validate this loss term with HM.
%
As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining robustness (especially
intra-class-wise), while retaining an acceptable trade-off in R@1.

>>>>

\noindent\textbf{III. Intra-Class Structure.}
%
$L_\text{ICS}$ is independent to HM, but is incompatible with ACT as it does
not create adversarial anchor.
%
Thus, we validate this loss term with HM.
%
As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining higher robustness at a low training
cost, while retaining an acceptable trade-off in R@1.
